Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-04 paper/main.tex
add figs of gravity eq dynamic ver

>>>>

\section*{Appendix}
\subsection*{A. Gravity Equation}
\begin{figure}[htbp] 
    \centering
    \caption{Impacts of Russia's Export Restriction on Its Trade Partners' Roundwood Import Volume}
    \subfigure[][Coniferous]{\includegraphics*[bb=0 0 900 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/gravity_eq/Industrial_roundwood__coniferous__export_import_.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/gravity_eq/Industrial_roundwood__non-coniferous_non-tropical__export_import_.png"}}
    \subfigure[][Non-coniferous]{\includegraphics*[bb=0 0 900 650, scale=0.15]{"~/OneDrive - The University of Tokyo/deforestation/fig/gravity_eq/Industrial_roundwood__non-coniferous_tropical__export_import_.png"}}
    \caption*{\small{The figure shows impacts of Russia's export restriction policy in 2007 on their trade partners' import volumne of coniferous roundwood (a), non-coniferous non-tropical roundwood (b), and non-coniferous tropical roundwood (c). X axis represents ellapesed time from the policy intervention. Thus, t = 0 means 2007. Y axis is the estimates of ATT. The black lines represent the point estimates and gray shadows represnt 95\% confidence interval.}}
    \label{fig:competitor_prod_Myanmar}
\end{figure}
